\textmd{\hmwkClass:\ \hmwkTitle}\\

### 2017-05-18 paper/main.tex
General edit

\newcommand{\hmwkTitle}{Extensible Physics Engine}
% \newcommand{\hmwkIssueDate}{22 February 2017}
\newcommand{\hmwkDueDate}{8 May 2017}
\newcommand{\hmwkClass}{6.905/6.945 Final Project Draft}
% \newcommand{\hmwkClassInstructor}{Professor Gerry Sussman}
\newcommand{\hmwkAuthorName}{\textbf{Michael Chang, Abigail Choe, Leon Shen}}

\title{
    \textmd{\hmwkClass:\ \hmwkTitle}\\
    % \normalsize{\hmwkClassInstructor}\\
    % \small{Issued\ on\ \hmwkIssueDate}\\
    \small{Due\ on\ \hmwkDueDate}
}
\author{\hmwkAuthorName}
\date{}
\begin{document}
\maketitle
\section{Introduction}

@@

This extension was made to allow our system to operate on any $n$th dimension
vector, and therefore be applicable to any $n$th dimension world
representation. For example, though the examples in this paper concern 2-dimensional worlds, the physics can easily be extended to 3-dimensinoal worlds. The default velocity of an object is set to 0 if it is not
specified. Supporting arithmetic operations between a scalar and a vector
enables our system to use a single default value 0 that is compatible with any
vector instead of limiting our system to the dimension of the default zero
vector specified.

>>>>

\newcommand{\hmwkTitle}{Extensible Physics Engine}
% \newcommand{\hmwkIssueDate}{22 February 2017}
%\newcommand{\hmwkDueDate}{8 May 2017}
\newcommand{\hmwkClass}{6.905/6.945 Final Project Draft}
% \newcommand{\hmwkClassInstructor}{Professor Gerry Sussman}
\newcommand{\hmwkAuthorName}{\textbf{Michael Chang, Abigail Choe, Leon Shen}}

\title{
    \textmd{\hmwkClass:\ \hmwkTitle}\\
    % \normalsize{\hmwkClassInstructor}\\
    % \small{Issued\ on\ \hmwkIssueDate}\\
    %\small{Due\ on\ \hmwkDueDate}
}
\author{\hmwkAuthorName}
\date{}
\begin{document}
\maketitle
\section{Introduction}

@@

This extension was made to allow our system to operate on any $n$th dimension
vector, and therefore be applicable to any $n$th dimension world
representation. For example, though the examples in this paper concern 2-dimensional worlds for easy graphic display, the physics can easily be extended to 3-dimensinoal worlds and beyond. The default velocity of an object is set to 0 if it is not
specified. Supporting arithmetic operations between a scalar and a vector
enables our system to use a single default value 0 that is compatible with any
vector instead of limiting our system to the dimension of the default zero
vector specified.
